Clustering exploration for `r params$sample_id`

### 2024-11-18 analyses/cell-type-wilms-tumor-06/notebook_template/02b_label-transfer_fetal_kidney_reference_Stewart.Rmd
fix typos in 00b and 02b, and re-render 00b

For some reason, the "cap-mesenchyme cells" has been renamed in cellxgene in "mesenchymal cells".

The cap mesenchyme is a cap of condensed metanephric mesenchyme, comprised of cells which epithelialize and sequentially form the pretubular aggregate (PA), renal vesicle (RV), C-, and S-shaped bodies, and finally the mature nephron. 
The CM contains nephron progenitor cells.

@@

- the fetal nephron / mesenchymal cells are cap-mesenchyme cells. 
In our case, cap-mesenchyme contains blastema and primitive epitheliul cancer cells.

- the stroma / mesenchymal stem are likelly mesenchymal cancer or normal cells.

>>>>

For some reason, the "cap-mesenchyme cells" has been renamed in CELLxGENE as "mesenchymal cells".

The cap mesenchyme is a cap of condensed metanephric mesenchyme, comprised of cells which epithelialize and sequentially form the peritubular aggregate (PA), renal vesicle (RV), C-, and S-shaped bodies, and finally the mature nephron. 
The CM contains nephron progenitor cells.

@@

- the fetal nephron / mesenchymal cells are cap-mesenchyme cells. 
In our case, cap-mesenchyme contains blastema and primitive epithelial cancer cells.

- the stroma / mesenchymal stem are likely mesenchymal cancer or normal cells.

### 2024-11-18 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd

#### Visualize seurat clusters and metadata

@@

#### Visualize seurat clusters and markers genes

@@

- `data` seurat object
- `first_group` is the name of the first metadata to group the cells
- `last_group` is the name of the second metadata to group the cells

@@

### Visualize seurat clusters

@@

#### TP53 pathway

here we will calculate a TP53 score using `AddModuleScore` and the genes of the HALLMARK_P53_PATHWAY gene set.

@@

### Find marker genes for each of the seurat clusters

>>>>

#### Visualize Seurat clusters and metadata

@@

#### Visualize Seurat clusters and markers genes

@@

- `data` Seurat object
- `first_group` is the name of the first metadata to group the cells
- `last_group` is the name of the second metadata to group the cells

@@

### Visualize Seurat clusters

@@

#### `TP53` pathway

here we will calculate a `TP53` score using `AddModuleScore` and the genes of the HALLMARK_P53_PATHWAY gene set.

@@

### Find marker genes for each of the Seurat clusters
